## Reference Libraries

```{r, message=F, warning=F}
library(dplyr, quietly = TRUE)
library(salesforcer, quietly = TRUE)
library(sqldf, quietly = TRUE)
library(gt, quietly = TRUE)
library(ggplot2, quietly = TRUE)
library(knitr)
library(scales, quietly = TRUE)
```

```{r, echo=F}
sf_auth()

last_week_proposals <- sprintf("SELECT Id, Name, HRA_Fees_Proposed__c, Office__c, PICText__c, Project_Manager__c, Proposal_Due_Date__c, Proposal_Type__c, Probability_of_Win__c, Anticipated_Budget_Range__c, Source__c FROM Project__c WHERE Stage__c = 'Proposal' AND Status__c NOT IN ('Dropped') AND Proposal_Due_Date__c >= 2020-09-27 AND Proposal_Due_Date__c <= 2020-10-03 ORDER BY Proposal_Due_Date__c")
proposals_query <- sf_query(last_week_proposals)

proposals <- sqldf("SELECT Id AS ID, Name as Project, Office__c AS Office, HRA_Fees_Proposed__c AS Fees FROM proposals_query")
```
---
title: 'Last Week's Proposal Analysis'
author: "Alex Sessums"
date: `r Sys.Date()`
output: html_document
---

```{r setup, include=F, warning=F}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown Notebook Sample
# Metrics Tracking - Last Week's Proposal Analysis
*Produced on `r Sys.Date()`*

This is a demonstration of an R Markdown document. Markdown is a simple tool for authoring reproducible HTML, PDF, and MS Word documents. For more details on using R Markdown as an Analytics tool, you can reference the RStudio website at <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r proposals_query}
summary(proposals_query)
```

# Sharing Reproducible Data

Here is an example of automated analysis:

Last week, the firm submitted `r nrow(proposals)` proposals submitted worth `r format(sum(proposals$Fees), scientific = FALSE)`, or `r format(sum(proposals$Fees) / nrow(proposals), scientific = FALSE)` per proposal. 

# Including Plots

You can also embed plots and graphs like this:

```{r fig.width = 3.5, fig.height = 5, echo = FALSE}
p <- proposals %>%
  group_by(Office)

ggplot(title = 'Proposal $ by Office', data=p, aes(x = Office, y = Fees)) + 
  scale_y_continuous(labels = comma) +
  geom_bar(stat="identity", fill = "steelblue") +
  geom_text(aes(label = Fees), vjust=1.6, color = "white", position = position_dodge(.9), size = 3.5) + theme_minimal() + ggtitle("Proposal $ by Office")
```

# Including Tables

Tables can also be easily produced and formatted like this:

```{r echo = FALSE}
knitr::kable(
  head(proposals[,1:4]), align = 'l', caption = 'Last Weeks Proposals',
  booktabs = TRUE)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
